The connection between star formation rate and dark matter halo mass in the epoch of reionization

### 2015-04-29 paper/ms.tex
editando intro observacional

The data from the Hubble Space Telescope Legacy (HSTL)
\citep{Bouwens15} is a compilation   of observations since the
installation of the Advanced Camera for Surveys (ACS) in 2002,
through the near-infrared Wide Field Camera 3 (WFC3/IR) installed in
2009, up to 2012.

The HST fields of view are: XDF, HUDF09-1, HUDF09-2, CANDELS-S/Deep, 
CANDELS-S/Wide, ERS, CANDELS-N/Deep, CANDELS-N/Wide, CANDELS-UDS, 
CANDELS-COSMOS and CANDELS-EGS, with areas of 4.7, 4.7, 4.7, 64.5, 34.2, 
40.5, 62.9, 60.9, 151.2, 151.9 and 150.7 arcmin$^2$ respectively. The total area 
at redshift 6 corresponds 
to 740.8 arcmin$^2$ over five different lines of sight, wit a total volume of 
$1.8 \times 10^6 \textrm{Mpc}^3$.
Two cameras performed the observations: ACS and WFC3/IR, using 
$B_{435}$, $V_{606}$, $ i_{814}$, $ z_{850}$, $ I_{814}$, $Y_{098}$, $Y_{105}$, 
$J{125}$,  $JH_{140}$ and $H_{160}$ filters.
The limit magnitude is between $\sim27.5$mag in CANDELS-EGS and$\sim30 $mag in 
the  deepest field (XDF). Total number of z=6 LBG candidates is 940, most of 
them in the faint end of the LF, magnitudes in the rest frame are in the range 
$-22.52\leq M_{1600} \leq -16.77$ \citet{Bouwens15} calculated LF using a 
stepwise maximum-likelihood (SWML) based on \citet{Efstathiou88}. 
The Schechter parameters derived are: 
$\phi^* =(0.33_{-0.10}^{+0.15}) \times 10 ^{-3}  \textrm{Mpc}^{-3} $, 
$M^*_{1600} = -21.16\pm 0.20$ and $\alpha = -1.91 \pm 0.09$. 
\citet{Bouwens15} reported that using just few fields of view, UVLF has a 
slightly non-Schechter-like form.

\citet{Finkelstein14} worked also with HST, using the HUDF, CANDELS and GOODS 
fields, along with two of the Hubble Frontier Fields (HFF): deep parallel 
observations (unlensed fields) near the Abell 2744 and MACS J0416.1-2403 
clusters. The HFF uses the ACS and the WFC3/IR with the same filters 
aforementioned but $z_{850}$. Total survey area is around 
$\sim300\textrm{arcmin}^2$, with 706 photometric candidates at redshift 6 
defined as the interval $5.5<z<6.5$. Total volume of this study is around 
$ 8 \times 10^5 \textrm{Mpc}^3$. The Schechter function parameters they found 
are $\phi^* =(1.86_{-0.80}^{+0.94}) \times 10 ^{-4}  \textrm{Mpc}^{-3} $, 
$M^*_{1600} = -21.1_{-0.31}^{+0.25}$ and $\alpha = -2.02_{-0.10}^{+0.10}$.

>>>>

The data from the Hubble Space Telescope Legacy (HSTL)
\citep{Bouwens15} is a compilation  of observations taken with the
Advanced Camera for Surveys (ACS) and near-infrared Wide Field Camera
3 (WFC3/IR) since 2002 through 2012.

The information in that study comes from the ACS and WFC3/IR using the
filter $B_{435}$, $V_{606}$, $ i_{814}$, $ z_{850}$, $ I_{814}$, $Y_{098}$, $Y_{105}$,
$J{125}$,  $JH_{140}$ and $H_{160}$.
The study inclues the following fields of view. XDF,
HUDF09-1, HUDF09-2, CANDELS-S/Deep,  CANDELS-S/Wide, ERS,
CANDELS-N/Deep, CANDELS-N/Wide, CANDELS-UDS,  CANDELS-COSMOS and
CANDELS-EGS, with areas of 4.7, 4.7, 4.7, 64.5, 34.2,  40.5, 62.9,
60.9, 151.2, 151.9 and 150.7 arcmin$^2$ respectively.  
The total area  at redshift 6 corresponds to 740.8 arcmin$^2$ over
five different lines of sight, with a total estimated volume of  $1.8 \times
10^6 \textrm{Mpc}^3$ comoving.

The limit magnitude ranges between $\sim27.5$mag in CANDELS-EGS and
$\sim30 $mag in  the  deepest field (XDF). 
The total number of $z=6$ LBG candidates is $940$, most of 
them in the faint end of the LF given the relativeley small survey volume.
The restframe UV magnitudes for these candidates are in the range.
$-22.52\leq M_{1600} \leq -16.77$.
\citet{Bouwens15} estimated the Luminosity Function (LF) using a 
stepwise maximum-likelihood (SWML) based on \citet{Efstathiou88}. 
They obtained the following Schechter parameters:
$\phi^* =(0.33_{-0.10}^{+0.15}) \times 10 ^{-3}  \textrm{Mpc}^{-3} $, 
$M^*_{1600} = -21.16\pm 0.20$ and $\alpha = -1.91 \pm 0.09$. 
\citet{Bouwens15} notes that only using few fields of view can yield a
LF with a deviations from the Schechter shape.

\citet{Finkelstein14} worked also with HST, using the HUDF, CANDELS and GOODS 
fields, along with two of the Hubble Frontier Fields (HFF) of deep parallel 
observations (unlensed fields) near the Abell 2744 and MACS J0416.1-2403 
clusters. 
The HFF uses the ACS and the WFC3/IR with the same filters
aforementioned but $z_{850}$. Total survey area is around  
$\sim300\textrm{arcmin}^2$, with 706 photometric candidates at redshift 6 
defined as the interval $5.5<z<6.5$. Total volume of this study is around 
$ 8 \times 10^5 \textrm{Mpc}^3$. The Schechter function parameters they found 
are $\phi^* =(1.86_{-0.80}^{+0.94}) \times 10 ^{-4}  \textrm{Mpc}^{-3} $, 
$M^*_{1600} = -21.1_{-0.31}^{+0.25}$ and $\alpha = -2.02_{-0.10}^{+0.10}$.
